Constructing a universe for the setoid model

### 2020-01-20 types20-abstract.tex
Updated author list.

\title{Constructing a universe for the setoid model}
\titlerunning{Constructing a universe for the setoid model}
\authorrunning{Altenkirch, Kaposi, Sestini}

\author{Thorsten Altenkirch\inst{1}\thanks{Supported by USAF grant
    FA9550-16-1-0029.} \and Ambrus Kaposi \inst{2} \and Filippo Sestini\inst{1}}

\institute{
  School of Computer Science, University of Nottingham, UK\\
  \email{\{psztxa,psxfs5\}@nottingham.ac.uk}
  \and
  E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary\\
  \email{akaposi@inf.elte.hu}
}

>>>>

\title{Constructing a universe for the setoid model}
\titlerunning{Constructing a universe for the setoid model}
\authorrunning{Altenkirch, Kaposi, Sattler, Sestini}

\author{
  Thorsten Altenkirch \inst{1}\thanks{Supported by USAF grant FA9550-16-1-0029.}
\and
  Ambrus Kaposi \inst{2}
\and
  Christian Sattler\inst{1}\thanks{Supported by USAF grant FA9550-16-1-0029.}
\and
  Filippo Sestini\inst{1}
}

\institute{
  School of Computer Science, University of Nottingham, UK\\
  \email{\{psztxa,pszcs1,psxfs5\}@nottingham.ac.uk}
  \and
  E{\"o}tv{\"o}s Lor{\'a}nd University, Budapest, Hungary\\
  \email{akaposi@inf.elte.hu}
}
